\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[spanish,activeacute]{babel}

\title{Titulo}
\author{Autor}

\begin{document}

\maketitle

\section{Secciones}
\subsection{Subsecciones}

asdasd asdasd

asdasd
asd

\section{Deep Learning}
\subsection{Introduction}
Introduction to deep learning goes here. You can add your text, equations, and images as needed.

\subsection{Deep Learning Fundamentals}
Fundamentals of deep learning, including neural networks and backpropagation, go here. You can add your text, equations, and images as needed.

\subsection{Applications of Deep Learning}
Applications of deep learning, including computer vision and natural language processing, go here. You can add your text, equations, and images as needed.

\end{document}
\begin{abstract}
Machine learning is a subset of artificial intelligence that involves the use of algorithms and statistical models to enable machines to perform tasks without being explicitly programmed. This article will explore the fundamentals of machine learning, including supervised and unsupervised learning, deep learning, and neural networks. We will also discuss the applications of machine learning in various fields, such as computer vision, natural language processing, and predictive analytics. Additionally, we will examine the current challenges and limitations of machine learning, as well as future directions for research and development.
\end{abstract}
\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[spanish,activeacute]{babel}

\title{Titulo}
\author{Autor}

\begin{document}

\maketitle

\section{Secciones}
\subsection{Subsecciones}

asdasd asdasd

asdasd
asd

\end{document}


